### 2016-01-18 paper.tex
Add filter width for RPM moving average

To calculate turbine RPM from shaft angle, the encoder signal is differentiated
using a second order central difference scheme, after which a relatively
small-windowed moving average smoothing filter is applied to match the noise
level present in the redundant turbine RPM measurement from the motion
controller. A similar approach is used for calculating tow carriage speed
$U_\infty$ from carriage position measurements. Power and drag coefficients are
calculated as instantaneous quantities from the carriage speed as

>>>>

To calculate turbine RPM from shaft angle, the encoder signal is differentiated
using a second order central difference scheme, after which an 8 sample wide
moving average smoothing filter is applied to match the noise level present in
the redundant turbine RPM measurement from the motion controller. A similar
approach is used for calculating tow carriage speed $U_\infty$ from carriage
position measurements. Power and drag coefficients are calculated as
instantaneous quantities from the carriage speed as
